\documentclass[11pt,letterpaper]{article}

\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage{palatino}
\linespread{1.05}

% Section formatting - line underneath
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

% No page numbers
\pagestyle{empty}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

% Custom list for bullet points with dashes
\newlist{cvitems}{itemize}{1}
\setlist[cvitems]{label=$-$, leftmargin=2em, topsep=2pt, itemsep=1pt, parsep=0pt}

\begin{document}

% Header
\noindent{\huge\bfseries Mourad Heddaya}\hfill{\normalsize \href{mailto:mourad@uchicago.edu}{mourad@uchicago.edu} $|$ \href{https://mheddaya.com}{mheddaya.com} $|$ 425-753-5800}
\vspace{2pt}
\hrule

%% Research Summary
\vspace{12pt}
\noindent \textbf{I'm interested in how we measure, evaluate, and design AI methods for open-ended problems where outcomes can be ambiguous and no clear ground truth exists. My work spans AI evaluation, reasoning, alignment, and human-AI interaction with applications across multiple domains.}

%% Education
\section*{Education}

\textbf{Ph.D. in Computer Science}, University of Chicago, 2021--2026 (expected May).\\
\hspace*{2em}\textit{Advisor: Chenhao Tan}

\vspace{4pt}

\textbf{B.S. in Informatics}, University of Washington, 2015--2019.\\
\hspace*{2em}\textit{Research Supervisors: Noah Smith \& Mari Ostendorf}

%% Publications
\section*{Selected Publications}
\vspace{4pt}
\begin{enumerate}[label={[\arabic*]}, leftmargin=2em, topsep=2pt, itemsep=1pt, parsep=0pt]
    \item \textbf{M.\ Heddaya}, R.\ Wadhawan, M.\ Roberts, C.\ Tan. \href{https://mheddaya.com/papers/acl2026_abridge.pdf}{When Internalization Fails: Finding Better Targets for Reasoning Compression.} Under review, \textit{ACL 2026}.
    \item \textbf{M.\ Heddaya}, K.\ MacMillan, A.\ Malani, H.\ Mei, C.\ Tan. \href{https://arxiv.org/abs/2501.00097}{CaseSumm: A Large-Scale Dataset for Long-Context Summarization.} \textit{Findings of NAACL 2025}. \textit{Accepted with talk @ \href{https://alea2024.github.io/}{ALEA 2024}}.
    \item \textbf{M.\ Heddaya}, C.\ Tan, R.\ Voigt, Q.\ Zeng, A.\ Zentefis. \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=5259107}{A Century of Inflation Narratives.} \textit{SSRN 2025}.
    \item \textbf{M.\ Heddaya}, Q.\ Zeng, C.\ Tan, R.\ Voigt, A.\ Zentefis. \href{https://aclanthology.org/2024.wnu-1.12/}{Causal Micro-Narratives.} \textit{WNU @ EMNLP 2024}.
    \item \textbf{M.\ Heddaya}, S.\ Dworkin, C.\ Tan, R.\ Voigt, A.\ Zentefis. \href{https://aclanthology.org/2023.acl-long.735/}{Language of Bargaining.} \textit{ACL 2023}.
\end{enumerate}

%% Research
\section*{Research}
\vspace{4pt}
\noindent{\large\textbf{PhD Student, University of Chicago CS}} \hfill 2021--2026
\begin{cvitems}
    \item Demonstrated that chain-of-thought internalization does not scale to complex reasoning [1]; proposed post-think distillation, a new compression target that preserves the teacher's solution path and achieves the best accuracy--efficiency trade-off on competition math.
    \item {[ongoing]} Built and deployed \href{https://civicchats.org}{\textbf{CivicChats.org}}, an AI platform for critical thinking \& civic deliberation with automated evaluation (CivicEval); running a large controlled experiment on ballot measure understanding. \href{https://open.substack.com/pub/cichicago/p/civicchats-building-ai-to-support}{[blog]}
    \item Developed a method for at-scale automatic extraction of causal narratives and applied it to 4.2M sentences from a century of U.S.\ inflation coverage [3]; found causal narratives predict consumer expectations and spread via contagion and differentiation.
    \item Built a 25.6K long-context understanding benchmark from Supreme Court opinion--summary [2]; showed automatic metrics diverge from expert judgment and fine-tuned models hallucinate more often than GPT-4, which hallucinates less but more subtly.
    \item Collected $\sim$400 human bargaining interactions with real incentives [5]; language reduces price variance 3$\times$ and simple linguistic features outperform transformers at predicting outcomes.
\end{cvitems}

\vspace{4pt}
\noindent{\large\textbf{ML Research Scientist Intern, \href{https://www.abridge.com}{Abridge AI}}} \hfill Summer 2025
\begin{cvitems}
    \item Developed methods for \textbf{reasoning compression} [1] in language models, identifying when internalization fails and finding better targets for distilling reasoning.
\end{cvitems}

\vspace{4pt}
\noindent{\large\textbf{Applied Scientist Intern, \href{https://aws.amazon.com/bedrock/}{Amazon AWS AI Labs (Bedrock)}}} \hfill Summer 2023
\begin{cvitems}
    \item Developed self-supervised alignment, a method for aligning LLMs to human preferences without RLHF, removing the need for reward models and reducing annotation requirements.
    \item The model scores its own outputs and uses self-feedback during fine-tuning as a regularizer for alignment.
\end{cvitems}

\vspace{4pt}
\noindent{\large\textbf{Research Engineer, University of Washington}} \hfill 2020--2021
\begin{cvitems}
    \item Industry collaboration building unsupervised \& supervised information extraction systems for conversational speech data (Advisors: Noah Smith \& Mari Ostendorf). \href{https://arxiv.org/abs/2205.12967}{[paper]}
\end{cvitems}

%% Other Papers
\section*{Other Papers \& Research Mentorship}

\begin{cvitems}
    \item J.\ Fu, \textbf{M.\ Heddaya}, C.\ Tan. \href{https://openreview.net/forum?id=d1PcXKaAON}{Automatically Generating Hard Math Problems from Hypothesis-Driven Error Analysis.} \textit{LLM Reasoning @ ICLR 2026}.
    \item C.\ Shah, A.\ Agarwal, K.\ Garg, \textbf{M.\ Heddaya}. \href{https://neurips.cc/virtual/2025/loc/san-diego/128019}{LLM Rationalis? Measuring Bargaining Capabilities of AI Negotiators.} \textit{MTI @ NeurIPS 2025}.
\end{cvitems}

%% Invited Talks
\section*{Invited Talks}

\textbf{Freestone Grove Partners}, April 2025 --- Causal Micro-Narratives.

\vspace{4pt}

\textbf{Max Planck Institute for Research on Collective Goods}, February 2025 --- NLP in the Legal Domain.

\vspace{4pt}

\textbf{University of Chicago LEAP Workshop}, January 2023 --- Language of Bargaining.

%% Teaching
\section*{Teaching}

\textbf{University of Chicago}\\
\hspace*{2em}\textit{CMSC 25400 -- Machine Learning, Winter 2023}\\
\hspace*{2em}\textit{CMSC 25300 / 35300 -- Mathematical Foundation of Machine Learning, Fall 2022}\\
\hspace*{2em}\textit{CMSC 35100 -- Natural Language Processing, Winter 2022}

\end{document}
